---
title: "Analysis"
author: "MIS COVID Task Force"
date: "4/3/2020"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries

```{r, include=FALSE, echo=FALSE}
library(tidyverse)
library(lubridate)

source("utils/covid.R")
source("utils/tex.R")
source("utils/plotting.R")
source("utils/bayes.R")
```


## Data

```{r}
df_pp <- read_csv("data/data_preprocessed.csv") 
stanDat_main <- make_stan_dat()
```


## Model

Load fit of the main model. To fit the model, run main.r.

```{r}
# Already fitted model
main_fit <- readRDS("fitted-models/base.rds")

# Main parameters of interes
main_fit$summary(c("mu_p_in", "sigma_p_in", "theta", "alpha_0", "phi_new_infections", "phi_new_cases", "lambda"))

# NPI names
npi_var <- as.character(1:7)
npi_names <- c("School closure", "Border closure", "Event ban", 
               "Gathering ban", "Venue closure", "Stay-at-home order", "Work ban")
names(npi_names) <- npi_var
npi_ranking <- rank(main_fit$summary(c("theta"))[["mean"]])
names(npi_ranking) <- npi_names

# Country x Country ID mapping
cid_country <- df_pp %>% group_by(country) %>% slice(1) %>% ungroup %>% dplyr::select(country, country_id)

# Choose credible interval for reporting
ci_interval <- mean_qi
```

## Main results

### NPIs 

#### Individual effects

```{r}
# NPI effect estimates (theta_m)
npi_main <- gather_draws(main_fit, theta[measure]) 

npi_main %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! npi_names))) %>%
  ci_interval() %>%
  arrange(desc(.value)) %>%
  mutate_if(is.numeric, function(x) round(x * 100)) %>%
  dplyr::select(measure, .lower, .value, .upper)

# Plot results
npi_pl <- npi_main %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! ifelse(npi_names == "Stay-at-home order", "\\hphantom{S}Stay-at-home order", npi_names)))) %>%
  rename(reduction = .value) %>%
  ggplot(aes(y = reorder(measure, reduction), x = reduction)) +
  stat_pointintervalh(point_interval = ci_interval, shape = 21, fill = "grey", color = "black", point_size = 2) +
  geom_vline(aes(xintercept = 0), color = "red", linetype = "dotted") +
  scale_x_continuous(expand = c(0,0), limits = c(NA, .77), labels = function(x) x * 100, breaks = seq(0,  1, .25)) +
  labs(x = "Estimated reduction (\\%)",
       y = "NPI") +
  theme_nature() +
  theme(axis.title.y = element_blank())

save_plot(npi_pl, "results/npi_effects.pdf", "results/npi_effects.tex")
```

#### Posterior ranking

```{r}
main_ranks <- npi_main %>%
  ungroup() %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! npi_names))) %>%
  mutate(.draw = rep(1:4000, 7)) %>%
  group_by(.draw) %>%
  mutate(est_rank = rank(-.value, ties = "first")) %>%
  ungroup() %>%
  group_by(measure, est_rank) %>%
  summarize(share_rank = n() / 4000 * 100) %>%
  ungroup() %>%
  mutate(measure = recode(measure, !!! npi_names)) %>%
  mutate(measure_order = recode(measure, !!! npi_ranking)) %>%
  mutate(est_rank = factor(est_rank, level = rev(as.character(1:length(npi_names)))))

ranks_pl <- main_ranks %>%
  mutate(measure = as.factor(ifelse(as.character(measure) == "Stay-at-home order", "\\hphantom{S}Stay-at-home order", as.character(measure)))) %>%
  ggplot(aes(y = reorder(measure, measure_order), x = share_rank, fill = est_rank)) +
  geom_bar(position = "stack", stat = "identity") +
  geom_vline(aes(xintercept = 50), linetype = "dashed") +
  scale_fill_brewer() +
  labs(y = "", x = "Estimated proportion (\\%)", fill = "Rank") +
  theme_nature() +
  theme(axis.title.y = element_blank(), legend.position = "bottom", legend.margin = unit(0,"cm")) +
  guides(fill = guide_legend(nrow = 1, byrow = T, reverse = T, keywidth = unit(0.4, "line"), keyheight = unit(0.2, "line")))

save_plot(ranks_pl, "results/npi_ranking.pdf", "results/npi_ranking.tex")
```

#### Combined effects

```{r}
# Total effect
npi_tot <- npi_main %>%
  ungroup() %>%
  group_by(.draw) %>%
  mutate(.value = 1 - .value) %>%
  summarize(.value = 1 - prod(.value)) %>%
  ungroup() %>%
  ci_interval()
npi_tot


# Number of effects greater 0 and 10 %
npi_k <- npi_main %>%
  ungroup() %>%
  group_by(.draw) %>%
  summarize(k0 = sum(.value > 0),
            k10 = sum(.value > 0.1)) %>%
  ungroup() 

# Summarize proportion >0
npi_prob_0 <- npi_k %>%
  group_by(k0) %>%
  summarize(prob = n() / 4000 * 100) %>%
  ungroup() %>%
  arrange(desc(k0)) %>%
  mutate(prob = cumsum(prob))
npi_prob_0 <- rbind(npi_prob_0, data.frame(k0 = c(1, 2), prob = c(100, 100)))


# Plot >0
npi_prob_0_pl <- npi_prob_0 %>%
  ggplot(aes(y = factor(k0), x = prob)) +
  geom_bar(stat = "identity") +
  geom_text(aes(y = k0, x = prob + 5, label = round_k(prob, 0)), color = "black", size = 8 / cm(1)) +
  geom_vline(aes(xintercept = 50), linetype = "dashed") +
  scale_x_continuous(expand = c(0,0), limits = c(0,120), breaks = seq(0, 120, 25)) +
  labs(y = "$m$ effects > 0\\%", x = "Estimated proportion (\\%)") +
  theme_nature() 

npi_prob_0_pl
save_plot(npi_prob_0_pl, "results/npi_prob_0.pdf", "results/npi_prob_0.tex")

# Summarize proportion >10
npi_prob_10 <- npi_k %>%
  group_by(k10) %>%
  summarize(prob = n() / 4000 * 100) %>%
  ungroup() %>%
  arrange(desc(k10)) %>%
  mutate(prob = cumsum(prob))
npi_prob_10 <- rbind(npi_prob_10, data.frame(k10 = c(1, 7), prob = c(100, 0)))

# Plot >10
npi_prob_10_pl <- npi_prob_10 %>%
  ggplot(aes(y = factor(k10), x = prob)) +
  geom_bar(stat = "identity") +
  geom_text(aes(y = k10, x = prob + 5, label = round_k(prob, 0)), color = "black", size = 8 / cm(1)) +
  geom_vline(aes(xintercept = 50), linetype = "dashed") +
  scale_x_continuous(expand = c(0,0), limits = c(0,120), breaks = seq(0, 120, 25)) +
  labs(y = "$m$ effects > 10\\%", x = "Estimated proportion (\\%)") +
  theme_nature() 

npi_prob_10_pl
save_plot(npi_prob_10_pl, "results/npi_prob_10.pdf", "results/npi_prob_10.tex")
```

### Model fit

```{r}
expected_N <- gather_draws(main_fit, E_new_cases_rep[day, country])
expected_I <- gather_draws(main_fit, E_new_infections_rep[day, country])

pdf("results/compartments.pdf", width = 12 / cm(1), height = 10 / cm(1))
for (i in cid_country$country_id) {
  print(plot_compartments(cid_country$country[i], stanDat_main, expected_N, expected_I))
}
dev.off()
```

## Detailed estimation results

### Parameter estimates

```{r}
# Parameter estimates
alpha_0_ci <- gather_draws(main_fit, alpha_0) %>% ci_interval()
tau_ci <- gather_draws(main_fit, tau) %>% ci_interval()
alpha_j_ci <- gather_draws(main_fit, alpha_j[j]) %>% ci_interval()
theta_ci <- gather_draws(main_fit, theta[m]) %>% ci_interval()
lambda_ci <- gather_draws(main_fit, lambda) %>% ci_interval()
I0_ci <- gather_draws(main_fit, new_infections_EpiStart[j]) %>% ci_interval()
phi_new_cases_ci <- gather_draws(main_fit, phi_new_cases) %>% ci_interval()
phi_new_infections_ci <- gather_draws(main_fit, phi_new_infections) %>% ci_interval()
mu_p_in_ci <- gather_draws(main_fit, mu_p_in) %>% ci_interval() 
sigma_p_in_ci <- gather_draws(main_fit, sigma_p_in) %>% ci_interval()

par_est <- map_dfr(list(alpha_0_ci, tau_ci, alpha_j_ci, theta_ci, lambda_ci, I0_ci, phi_new_cases_ci, phi_new_infections_ci, mu_p_in_ci, sigma_p_in_ci),
                  function(par) data.frame(mean = par$.value, lower = par$.lower, upper = par$.upper))


# Neff Ratio
par_est$neff_ratio <- c(
  main_fit$summary(c("alpha_0"))[["ess_bulk"]],
  main_fit$summary(c("tau"))[["ess_bulk"]],
  main_fit$summary(c("alpha_j"))[["ess_bulk"]],
  main_fit$summary(c("theta"))[["ess_bulk"]],
  main_fit$summary(c("lambda"))[["ess_bulk"]],
  main_fit$summary(c("new_infections_EpiStart"))[["ess_bulk"]],
  main_fit$summary(c("phi_new_cases"))[["ess_bulk"]],
  main_fit$summary(c("phi_new_infections"))[["ess_bulk"]],
  main_fit$summary(c("mu_p_in"))[["ess_bulk"]],
  main_fit$summary(c("sigma_p_in"))[["ess_bulk"]]) / 4000

# Rhat
par_est$rhat <- c(
  main_fit$summary(c("alpha_0"))[["rhat"]],
  main_fit$summary(c("tau"))[["rhat"]],
  main_fit$summary(c("alpha_j"))[["rhat"]],
  main_fit$summary(c("theta"))[["rhat"]],
  main_fit$summary(c("lambda"))[["rhat"]],
  main_fit$summary(c("new_infections_EpiStart"))[["rhat"]],
  main_fit$summary(c("phi_new_cases"))[["rhat"]],
  main_fit$summary(c("phi_new_infections"))[["rhat"]],
   main_fit$summary(c("mu_p_in"))[["rhat"]],
  main_fit$summary(c("sigma_p_in"))[["rhat"]])

# Generate tex table
par_est$par <- c("$\\alpha$", "$\\tau$", paste0("$\\alpha_{", 1:20, "}$"), paste0("$\\theta_", 1:7, "$"), 
                 "$\\lambda$", paste0("$I_{", 1:20, "\\,", -33, "}$"), "$\\phi^N$", "$\\phi^I$", "$\\mu^{p_{IN}}$",  "$\\sigma^{p_{IN}}$")
par_est <- dplyr::select(par_est, par, mean, lower, upper, neff_ratio, rhat)

xtable::print.xtable(
  file = "results/EstimationResults.tex",
  xtable::xtable(
    par_est
  ),
  only.contents = T,
  include.colnames = F,
  include.rownames = F,
  sanitize.text.function = identity,
  hline.after = NULL
)
```

### Time from infection to reporting

```{r}
post_mu_p_in <- gather_draws(main_fit, mu_p_in) %>% ungroup()
post_mu_p_in_pl <- ggplot() + 
  geom_line(data = data.frame(x = seq(1, 5, .001), y = dnorm(seq(1, 5, .001), 2.5, 0.5)), mapping = aes(x = x, y = y), color = "skyblue3") +
  geom_density(data = post_mu_p_in, mapping = aes(x = .value), col = "tomato3") +
  geom_vline(aes(xintercept = mean(post_mu_p_in$.value)), col = "tomato3", linetype = "dashed") +
  geom_vline(aes(xintercept = 2.5), col = "skyblue3", linetype = "dashed") +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 5), breaks = seq(0, 5, 1)) +
  labs(x = expression(mu), y = "Density") +
  theme_nature()
post_mu_p_in_pl
save_plot(post_mu_p_in_pl, pdf_file = "results/mu_p_in.pdf")

post_sigma_p_in <- gather_draws(main_fit, sigma_p_in) %>% ungroup()
sigma_p_in_pl <- ggplot() + 
  geom_line(data = data.frame(x = seq(0, 2, .001), y = dgamma(seq(0, 2, .001), 2, 2 / 0.4)), mapping = aes(x = x, y = y), color = "skyblue3") +
  geom_density(data = post_sigma_p_in, mapping = aes(x = .value), col = "tomato3") +
  geom_vline(aes(xintercept = mean(post_sigma_p_in$.value)), col = "tomato3", linetype = "dashed") +
  geom_vline(aes(xintercept = 0.4), col = "skyblue3", linetype = "dashed") +
  scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 2), breaks = seq(0, 2, 0.4)) +
  labs(x = expression(sigma), y = "Density") +
  theme_nature()
sigma_p_in_pl
save_plot(sigma_p_in_pl, pdf_file = "results/sigma_p_in.pdf")

posterior_p_in <- gather_draws(main_fit, p_in[x]) %>% 
  ungroup() %>%
  mutate(x = max(x) - x) %>%
  dplyr::filter(x <= 30) %>%
  group_by(x) %>%
  summarize(.lower = quantile(.value, 0.025),
            .upper = quantile(.value, 0.975),
            .mean = mean(.value)) %>%
  ungroup() 
prior_p_in <- data_delay(xT = 30, from0 = T, p_in, mu = rnorm(4000, 2.5, 0.5), sigma = rgamma(4000, 2, 2 / 0.4)) %>%
  group_by(x) %>%
  summarize(.lower = quantile(value, 0.025),
            .upper = quantile(value, 0.975),
            .mean = mean(value)) %>%
  ungroup() 
  
posterior_p_in_pl <- ggplot(data = rbind(posterior_p_in, prior_p_in) %>% mutate(type = rep(c("Posterior", "Prior"), each = 31)), 
                             mapping = aes(x = x, y = .mean, ymin = .lower, ymax = .upper, color = type, fill = type)) +
  geom_line(linetype = "dashed") +
  geom_ribbon(alpha = 0.2, color = "white") +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_manual(values = c("tomato3", "skyblue3"), name = "") +
  scale_color_manual(values = c("tomato3", "skyblue3"), name = "") +
  labs(y = "Prob. to be reported", x = "Days post infection") +
  theme_nature()
posterior_p_in_pl
save_plot(posterior_p_in_pl, pdf_file = "results/p_in.pdf")
``` 

### Influential observations

```{r}
main_loo_ll <- main_fit$draws("log_lik") %>% 
    apply(3, na.omit) %>%
    Filter(f = length) 
loo_cid <- sapply(stringi::stri_extract_all(names(main_loo_ll), regex = "\\d{1,2}"), function(x) x[[2]])
main_loo <- main_loo_ll %>% abind::abind(along = 3) %>% loo

plot(main_loo) 

loo_dat <- data.frame(country_id = as.numeric(loo_cid),
                      date = as.Date(unlist(sapply(stanDat_main$date, function(x) as.character(x[(stanDat_main$EpiStart+1):length(x)])))),
                      k = main_loo$diagnostics$pareto_k) %>%
  left_join(cid_country)

loo_pl <- loo_dat %>%
  ggplot(aes(x = date, y = k)) +
  geom_point(shape = 3) +
  facet_wrap(~ country, ncol = 4, scales = "free_x") +
  geom_hline(aes(yintercept = 0), linetype = "dashed", color = "black") +
  geom_hline(aes(yintercept = 0.5), linetype = "dashed", color = "red") +
  geom_hline(aes(yintercept = 0.7), linetype = "dashed", color = "red") +
  scale_y_continuous(limits = c(min(loo_dat$k)-0.05, ifelse(max(loo_dat$k) > 1, max(loo_dat$k), 1)), breaks = c(0, 0.5, 0.7)) +
  labs(y = "Pareto shape k", x = "Date") +
  theme_nature() 

save_plot(loo_pl, "results/influential_observations.pdf", w = 24, h = 20)
```

### Posterior pairs

```{r}
npi_main_theta <- npi_main %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! npi_names))) %>%
  ungroup() %>%
  mutate(.draw = rep(1:4000, 7)) %>%
  dplyr::select(measure, .value, .draw) %>%
  spread(measure, .value) %>%
  dplyr::select(`School closure`, `Border closure`, `Event ban`, `Gathering ban`, `Venue closure`, `Stay-at-home order`, `Work ban`)

cor(npi_main_theta) %>% round(2)

corr_pl <- ggpairs(npi_main_theta, 
                   lower = list(continuous = contours),
                   diag = list(continuous = wrap(hist_fun)),
                   upper = list(continuous = wrap(cor_fun, sz = text_size*5/14, stars = FALSE))) +
  theme_nature()

save_plot(corr_pl, pdf_file = "results/posterior_pairs.pdf", w = 20, h = 20)
```


## Sensitivity checks

### Start of modeling phase

```{r}
rc_ModelStartCases10 <- readRDS("robustness-checks/fitted-models/rc_ModelStartCases_10.rds")
rc_ModelStartCases50 <- readRDS("robustness-checks/fitted-models/rc_ModelStartCases_50.rds")

npi_rc_ModelStartCases10 <- gather_draws(rc_ModelStartCases10, theta[measure])
npi_rc_ModelStartCases50 <- gather_draws(rc_ModelStartCases50, theta[measure])

npi_rc_ModelStartCases_pl <- plot_rc(list(npi_rc_ModelStartCases10, npi_rc_ModelStartCases50, npi_main), 
                                     color_levs = c("10", "50", "100"), default = c(F, F, T), color_lab = "Cumulative cases until start of modeling phase")

save_plot(npi_rc_ModelStartCases_pl, pdf_file = "robustness-checks/results/rc_ModelStartCases.pdf", w = 14, h = 11)

remove(rc_ModelStartCases10, rc_ModelStartCases50)
```

### End of modeling phase

```{r}
rc_EpidemicEnd_1 <- readRDS("robustness-checks/fitted-models/rc_EpidemicEnd_21.rds")
rc_EpidemicEnd_2 <- readRDS("robustness-checks/fitted-models/rc_EpidemicEnd_35.rds")

npi_rc_EpidemicEnd_1 <- gather_draws(rc_EpidemicEnd_1, theta[measure]) 
npi_rc_EpidemicEnd_2 <- gather_draws(rc_EpidemicEnd_2, theta[measure]) 

npi_rc_EpidemicEnd_pl <- plot_rc(list(npi_rc_EpidemicEnd_1, npi_main, npi_rc_EpidemicEnd_2),
                                 color_levs = c("21", "28", "35"), default = c(F, T, F), color_lab = "Days since last NPI until end of modeling phase")

save_plot(npi_rc_EpidemicEnd_pl, pdf_file = "robustness-checks/results/rc_EpidemicEnd.pdf", w = 14, h = 11)

remove(rc_EpidemicEnd_1, rc_EpidemicEnd_2)
```


### Splines

```{r}
rc_spline_1 <- readRDS("robustness-checks/fitted-models/rc_ta_-1_tb_1.rds")
rc_spline_2 <- readRDS("robustness-checks/fitted-models/rc_tb_1.rds")
rc_spline_3 <- readRDS("robustness-checks/fitted-models/rc_tb_5.rds")

npi_rc_spline_1 <- gather_draws(rc_spline_1, theta[measure]) 
npi_rc_spline_2 <- gather_draws(rc_spline_2, theta[measure]) 
npi_rc_spline_3 <- gather_draws(rc_spline_3, theta[measure]) 

npi_rc_spline <- plot_rc(list(npi_rc_spline_1, npi_rc_spline_2, npi_main, npi_rc_spline_3),
                         color_levs = c("(-1,1)", "(0,1)", "(0,3)", "(1,5)"), default = c(F, F, T, F), color_lab = expression("First-order spline: FOS(t"[0]*", t"[1]*")")) 

save_plot(npi_rc_spline, pdf_file = "robustness-checks/results/rc_spline.pdf", w = 14, h = 13)

remove(rc_spline_1, rc_spline_2, rc_spline_3)
```

### Prior for theta_m

```{r}
rc_theta_1 <- readRDS("robustness-checks/fitted-models/rc_theta_mix_0.3.rds")
rc_theta_2 <- readRDS("robustness-checks/fitted-models/rc_theta_mix_0.5.rds")

npi_rc_theta_1 <- gather_draws(rc_theta_1, theta[measure]) 
npi_rc_theta_2 <- gather_draws(rc_theta_2, theta[measure]) 

npi_rc_theta <- plot_rc(list(npi_main, npi_rc_theta_1, npi_rc_theta_2), 
                        color_levs = c("10", "30", "50"), default = c(T, F, F), color_lab = "Prior probability of a negative effect of NPIs (%)") 

save_plot(npi_rc_theta, pdf_file = "robustness-checks/results/rc_theta.pdf", w = 14, h = 11)

remove(rc_theta_1, rc_theta_2)
```


### p_IN: Distribution for the time from infection to reporting

```{r}
par_p_in_est <- expand.grid(mu_mu0 = c(eval(formals(p_in)$mu) - 0.25, eval(formals(p_in)$mu), eval(formals(p_in)$mu) + 0.25), 
                            sigma_beta0 = c(eval(formals(p_in)$sigma) - 0.2, eval(formals(p_in)$sigma), eval(formals(p_in)$sigma) + 0.2))
par_p_in_est$mu_sigma0 <- 0.5
par_p_in_est$sigma_alpha0 <- 2
par_p_in_est_spec <- c()
npi_rc_p_in_est <- list()
for (i in 1:nrow(par_p_in_est)) {
  f <- paste0("robustness-checks/fitted-models/rc_p_in_mu_mu0_", round(par_p_in_est$mu_mu0[i], 2), "_p_in_mu_sigma0_", round(par_p_in_est$mu_sigma0[i], 2), 
              "_p_in_sigma_alpha0_", round(par_p_in_est$sigma_alpha0[i], 2), "_p_in_sigma_beta0_", round(par_p_in_est$sigma_beta0[i], 2), ".rds")
  par_p_in_est_spec[i] <- paste0("(Normal(", round(par_p_in_est$mu_mu0[i], 2), ", ", round(par_p_in_est$mu_sigma0[i], 2), "),\n",
                                 "Gamma(", round(par_p_in_est$sigma_alpha0[i], 2), ", ", round(par_p_in_est$sigma_beta0[i], 2), "))")
  npi_rc_p_in_est[[i]] <- gather_draws(readRDS(f), theta[measure]) 
}

npi_rc_p_in <- plot_rc(npi_rc_p_in_est, 
                        color_levs = par_p_in_est_spec, default = c(F, F, F, F, T, F, F, F, F),
                        color_lab = expression("p"[IN]*" ~ Lognormal("*mu*", "*sigma*")")) +
  theme(legend.spacing.y = unit(-0.25, "cm")) +
  guides(color = guide_legend(ncol = 3, byrow = T, override.aes = list(linetype = c(rep("solid", 4), "dashed", rep("solid", 4)))))
         
save_plot(npi_rc_p_in, pdf_file = "robustness-checks/results/rc_p_in_estimated.pdf", w = 14, h = 20)
```

### p_G: Generation time distribution

```{r}
par_p_g <- expand.grid(par1 = c(eval(formals(p_g)$p1) - 0.5, eval(formals(p_g)$p1), eval(formals(p_g)$p1) + 0.5),
                       par2 = c(eval(formals(p_g)$p2) - 1, eval(formals(p_g)$p2), eval(formals(p_g)$p2) + 1))
p_g_spec <- c()
npi_rc_p_g <- list()
for (i in 1:nrow(par_p_g)) {
  f <- paste0("robustness-checks/fitted-models/rc_par1_p_g_", round(par_p_g$par1[i], 2), "_par2_p_g_", round(par_p_g$par2[i], 2), ".rds")
  p_g_spec[i] <- paste0("(", round(par_p_g$par1[i], 2), ", ", round(par_p_g$par2[i], 2), ")")
  npi_rc_p_g[[i]] <- gather_draws(readRDS(f), theta[measure]) 
}

npi_rc_p_g_pl <- plot_rc(npi_rc_p_g, 
                          color_levs = p_g_spec, default = c(F, F, F, F, T, F, F, F, F),
                          color_lab = expression(p[G]*" ~ Gamma("*mu*", "*sigma*")")) +
  theme(legend.spacing.y = unit(-0.25, "cm")) +
  guides(color = guide_legend(ncol = 3, byrow = T, override.aes = list(linetype = c(rep("solid", 4), "dashed", rep("solid", 4)))))

save_plot(npi_rc_p_g_pl, pdf_file = "robustness-checks/results/rc_p_g.pdf", w = 14, h = 20)
```

### LOO country analysis

```{r}
# Load model and retrieve loo country theta estimates
loo_dat <- list()
for (cid in 1:max(df_pp$country_id)) {
  print(sprintf("Country %i | 20", cid))
  cid_fit <- readRDS(paste0("robustness-checks/fitted-models/rc_loo_", cid, ".rds"))
  loo_dat[[cid]] <- gather_draws(cid_fit, theta[measure])
  remove(cid_fit)
}
loo_dat <- do.call(rbind, loo_dat)
loo_dat <- loo_dat %>%
  ungroup() %>%
  mutate(country_id = as.numeric(rep(1:20, each = 7 * 4000)))  %>%
  left_join(cid_country, by = "country_id") %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! npi_names))) 

# Add degree to which NPIs were imposed by country
imposed_npis <- df_pp %>%
  dplyr::select(country, schools, borders, events, 
                gatherings, venues, lockdown, homeoffice) %>%
  set_names(c("country", npi_names)) %>%
  group_by(country) %>%
  summarize_all(max) %>%
  ungroup() %>%
  reshape2::melt(id.vars = "country") %>%
  rename(is_imposed = value, measure = variable)
  
loo_dat <- loo_dat %>% 
  dplyr::select(-country_id) %>%
  left_join(imposed_npis, by = c("country", "measure")) %>%
  mutate(measure = factor(measure, level = npi_names))

# Global estimate
global_dat <- npi_main %>%
  mutate(measure = as.factor(recode(as.character(measure), !!! npi_names))) %>%
  mutate(country = "Global")

# Plot
loo_dat_pl <- loo_dat %>%
  ggplot(aes(x = .value, y = country)) + # , color = is_imposed
  stat_pointintervalh(point_interval = ci_interval, position =  
                      ggstance::position_dodgev(height = .5), 
                      point_size = 1) +
  facet_wrap(~ measure, ncol = 3) +
  stat_pointintervalh(data = global_dat, mapping = aes(x = .value, y = country), color = "black",
                      point_interval = ci_interval, position =  
                      ggstance::position_dodgev(height = .5), 
                      point_size = 1) +
  geom_vline(aes(xintercept = 0), linetype = "dashed", color = "red") +
  scale_x_continuous(limits = c(NA,.7), labels = function(x) x * 100) +
  #scale_color_continuous(labels = function(x) x * 100) +
  labs(x = "Estimated reduction in new cases (%)", y = "Left-out country") + #, color = "Maximum cumulative share \n of population affected (%)") +
  theme_nature() +
  theme(legend.position = c(0.6, 0.15), legend.direction = "horizontal") 
  
save_plot(loo_dat_pl, "robustness-checks/results/rc_loo_country.pdf", w = 14, h = 18)
```

#### Split Australia

```{r}
rc_SeparateRegions_looA1 <- readRDS("robustness-checks/fitted-models/rc_separate_regions_loo_EA.rds")
rc_SeparateRegions_looA2 <- readRDS("robustness-checks/fitted-models/rc_separate_regions_loo_WA.rds")

npi_rc_SeparateRegions_looA1 <- gather_draws(rc_SeparateRegions_looA1, theta[measure])
npi_rc_SeparateRegions_looA2 <- gather_draws(rc_SeparateRegions_looA2, theta[measure])

npi_rc_SeparateRegions_loo_pl <- plot_rc(list(npi_main, npi_rc_SeparateRegions_looA1, npi_rc_SeparateRegions_looA2), 
                                     color_levs = c("None", "Eastern Australia", "Western Australia"), default = c(T, F, F), color_lab = "Left-out region")

save_plot(npi_rc_SeparateRegions_loo_pl, pdf_file = "robustness-checks/results/rc_SeparateRegions_looA1A2.pdf", w = 14, h = 11)

remove(rc_SeparateRegions_looA1, rc_SeparateRegions_looA2)
```

